Voice Classification by Neural Networks

### 2015-05-27 paper.tex
paper basically done except for cross-validation

\begin{abstract}
% TODO
% neural net to classify voice gender (age?)
%

In this paper, we describe a machine learning schema for voice classification by sex. We collected %XXXXX
voice samples that we used to train an artificial neural net with a single hidden layer using stochastic gradient descent. After experimenting to determine the optimal training parameters (number of iterations, etc.), using %%10-fold cross-validation with ROC AUC as our metric to evaluate our model.
With % certain settings
we were able to produce a model that performs %stats
\end{abstract}

@@

\subsection{Receiver Operating Characteristic (ROC)}

@@

This intuition suggests that a good metric for evaluating our models could be the area under the ROC curve.
Indeed, \emph{Area Under Curve} (AUC) is a common metric for binary classification.
Its value can range from 0 to 1, though in practice, our values will lie in $(0.5, 1)$.
A value of 0.5 corresponds to a model no better than a random classifier, while a value of 1 corresponds to a model that perfectly distinguishes between positive and negative instances.

@@

% ROC AUC scores and such

>>>>

\begin{abstract}
% TODO%

In this paper, we describe a machine learning schema for voice classification by sex.
We collected 63 voice samples (27 male, 36 female) that we used to train an artificial neural net with a single hidden layer using stochastic gradient descent.
After experimenting to determine the optimal training parameters, evaluating each ensemble of parameters with repeated random sub-sampling validation with ROC AUC as our evaluation metric, we arrived at a set of parameters that yielded a score of $0.929 \pm 0.010$ (error given as std. err. of mean).
\end{abstract}

@@

\subsection{Receiver Operating Characteristic (ROC)}
\label{subsec:roc}

@@

This intuition suggests that a good metric for evaluating our models could be the area under the ROC curve.
Indeed, \emph{Area Under Curve} (AUC) is a common metric for binary classification.
Its value can range from 0 to 1, though in practice, our values will lie in $(0.5, 1)$.
A value of 0.5 corresponds to a model no better than a random classifier (which has ROC curve $y = x$, and therefore an AUC of 0.5), while a value of 1 corresponds to a model that perfectly distinguishes between positive and negative instances.

@@

To evaluate our model and to optimize our parameters, we used repeated random sub-sampling validation for each ensemble of parameters we tested. For each of the 30 evaluation rounds, we set aside roughly 30\% of the data for testing. Each round produced an AUC score (see \cref{subsec:roc}); the average AUC score over all 30 rounds was used as the final score for the ensemble of parameters. Our final parameters (8 hidden nodes, 1000 stochastic gradient descent iterations, $\eta = 0.1$) yielded an average AUC score of $0.929 \pm 0.010$. \footnote{Error is given as standard error of the mean of all $N = 30$ AUC scores from the evaluation rounds, computed as $\f{\sigma}{\sqrt{N}}$, where $\sigma$ is the standard deviation of the AUC scores.}
